Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-05 WRITEUP/ms.tex
syntax

\AP{let us recall to make the note about different molecular tracers also here}

We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold.
That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds?

@@

This also implies that \obs with spatial resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies. Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. With the Next Generation VLA%
%mm2 (ngVLA
\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}, which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
% 0.005" highest freq
In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics, and
% mm2 subject to
    dependent on
the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.

@@

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Caitlin Casey for useful discussions.
%
TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
% mm
M-MML acknowledges partial support by the NSF through award
AST18-15461, and hospitality from the Insitute for Theoretical
Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
% mm2 We acknowledge use of the

\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PyMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}}
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.

>>>>

We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold.
That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds? 
Observationally, this effect would be mimicked by e.g., adopting different molecular gas tracers since they have different critical densities.

@@

This also implies that \obs with spatial resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies. Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. With the Next Generation VLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}, which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
% 0.005" highest freq
In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and depend on
the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.

@@

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Caitlin Casey for useful discussions.
%
TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
% mm
M-MML acknowledges partial support by the NSF through award
AST18-15461, and hospitality from the Insitute for Theoretical
Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PyMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and yt \citep{Smith09a,Turk11a}}
